% ============================================================
%  JGP_CV_v1_en.tex — Javier García Pinilla  (English)
%  Compilar con: pdflatex o xelatex
%  Online: overleaf.com → New Project → Upload
% ============================================================
\documentclass[12pt, a4paper]{article}

% ── Encoding & language ──────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

% ── Page ─────────────────────────────────────────────────────
\usepackage[
  top=1.6cm, bottom=1.4cm,
  left=2cm,  right=2cm
]{geometry}

% ── Typography ───────────────────────────────────────────────
\usepackage{ebgaramond}
% If ebgaramond is not available, comment above and uncomment:
% \usepackage{lmodern}

% ── Utilities ────────────────────────────────────────────────
\usepackage{parskip}
\setlength{\parskip}{0pt}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{xcolor}

\hypersetup{colorlinks=true, urlcolor=blue, hidelinks}
\pagestyle{empty}

\setlist[itemize]{leftmargin=1.5em, itemsep=0pt, parsep=0pt, topsep=2pt}

% ── Section with rule ────────────────────────────────────────
\newcommand{\seccion}[1]{%
  \vspace{7pt}%
  {\large\bfseries #1}%
  \vspace{1pt}%
  \hrule height 0.5pt%
  \vspace{2pt}%
}

% ── Experience entry ─────────────────────────────────────────
\newcommand{\trabajo}[4]{%
  \noindent\textbf{#1} \hfill \textbf{#2}\\
  \textit{#3} \hfill \textit{#4}%
  \vspace{1pt}%
}

% ── Education entry ──────────────────────────────────────────
\newcommand{\edu}[4]{%
  \noindent\textbf{#1} \hfill \textbf{#2}\\
  \textit{#3} \hfill \textit{#4}%
  \vspace{1pt}%
}

% ============================================================
\begin{document}
% ============================================================

% ── HEADER ──────────────────────────────────────────────────
{%
  \centering
  {\fontsize{24}{28.8}\selectfont\bfseries Javier García Pinilla}\par
  \vspace{1pt}
  {\fontsize{16}{19}\selectfont javiergarciapinilla95@gmail.com
    \quad|\quad +56\,9\,6748\,1782
    \quad|\quad Valparaíso, Chile}\par
  \vspace{1pt}
  \hrule height 0.5pt
\par}
\vspace{5pt}

% ── INTRODUCTION ────────────────────────────────────────────
\noindent
Data analyst with academic background in Computer Science Engineering,
Universidad de Chile. Top Analyst at Flipside Crypto and Data Alchemist at CovalentHQ,
with experience in on-chain analysis across multiple blockchain networks for
English-speaking communities. The same rigor applied to machine learning and data
automation. C1 English.

% ── WORK EXPERIENCE ─────────────────────────────────────────
\seccion{WORK EXPERIENCE}

\trabajo{Duran Alta Gestión SPA}{2025 -- 2026}{IT Services Consultant}{El Melón, Chile}
\begin{itemize}
  \item Designed Excel templates and standardized workflows to resolve frequent
        spreadsheet errors, improving data accuracy and reducing dependency on IT support.
  \item Developed troubleshooting guides that enabled the accounting team to manage
        common issues autonomously, increasing operational efficiency.
\end{itemize}
\vspace{2pt}

\trabajo{FlipsideCrypto}{2021 -- 2025}{Blockchain Data Analyst}{Remote}
\begin{itemize}
  \item Built interactive dashboards and data models to clarify complex on-chain
        information, facilitating interpretation of key metrics and decision-making.
  \item Prepared accessible reports and analyses for diverse audiences, increasing
        public interest and visits to associated websites.
\end{itemize}
\vspace{2pt}

\trabajo{GSG Group}{2019 -- 2021}{Executive Assistant}{Remote}
\begin{itemize}
  \item Managed calendars, meeting coordination, and operational workflows for
        C-suite executives, optimizing availability and internal organization.
  \item Improved administrative Excel templates and optimized internal processes,
        enabling clearer communication and efficient task tracking.
\end{itemize}

% ── CERTIFICATIONS ──────────────────────────────────────────
\seccion{CERTIFICATIONS}

\begin{tabularx}{\textwidth}{@{} X X @{}}
  Data Analysis \textbar{} Google Coursera                  & Advanced Data Analysis \textbar{} SENCE               \\[2pt]
  Project Management \textbar{} Google Coursera             & Data Science \textbar{} Alura Latam                   \\[2pt]
  AI \& Productivity \textbar{} Google                      & Blockchain Analysis \textbar{} CovalentHQ             \\[2pt]
  Marketing and SEO \textbar{} Santander Open Academy       & Power BI Masterclass \textbar{} Alura Latam            \\[2pt]
  English Certificate C1 \textbar{} EF SET                  & Power BI + AI \textbar{} Daxus Latam                  \\[2pt]
  Administrative Assistant \textbar{} Pareto Talent         & Oracle Cloud Foundations \textbar{} Oracle            \\[2pt]
  Hackathon Alura Latam ONE \textbar{} No Country           &                                                       \\
\end{tabularx}

% ── EDUCATION ───────────────────────────────────────────────
\seccion{EDUCATION}

\edu{Universidad de Chile}{2014 -- 2020}%
    {Computer Science Engineering}{Santiago, Chile}

\noindent\small Common Core completed + specialization courses (incomplete studies)
\vspace{4pt}

\edu{Colegio Cervantino}{2009 -- 2013}%
    {High School Diploma}{Putaendo, Chile}

% ── SKILLS ──────────────────────────────────────────────────
\seccion{SKILLS}

\begin{tabularx}{\textwidth}{@{} >{\bfseries}l X @{}}
  Software      & SQL \textbullet{} Python \textbullet{} Google Workspace \textbullet{}
                  Microsoft Office \textbullet{} Power BI \textbullet{} Tableau \textbullet{}
                  LLMs \textbullet{} GitHub \textbullet{} SAP \\[3pt]
  Methodologies & Project Management \textbullet{} Scrum \textbullet{} Kanban \textbullet{}
                  RACI Charts \textbullet{} Gantt \textbullet{} Agile and Waterfall
                  Methodologies \\[3pt]
  Languages     & Spanish (Native) \textbullet{} English C1 (Advanced) \\
\end{tabularx}

% ============================================================
\end{document}
